### 2021-07-24 paper.tex
fixed space for ranges
convolutional layer added in methodology, user classification

@@

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

% bibliography
\usepackage[
	%backend=biber,
	style=numeric,
	citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

			\begin{equation}
				E = \sum^{N_g - 1}_{i=0} \sum^{N_g - 1}_{j=0} p(i, j)^2 \
				\textnormal{ here, range = [0,1] }
			\end{equation}

@@

			\begin{equation}
				Con = \sum^{N_g -1}_{n=0} n^2 \sum^{N_g -1}_{i=0} \sum^{N_g
				-1}_{j=0} p(i,j)^2 \
				\textnormal{ here, range = [0,1] }
			\end{equation}

@@

			\begin{equation}
				C = \frac{1}{\sigma^x \sigma^y}
				\sum^{N_g - 1}_{i=0} \sum^{N_g -1}_{j=0} (i,j) p(i,j)^2
				- \mu_x \mu_y \ \textnormal{here, range = [-1,1]}
			\end{equation}

@@

	The Machine learning algorithms are used for
	classification of MR brain image either as normal or abnormal.  The major
	aim of ML algorithms is to automatically learn and make intelligent
	decisions. The feature set formed by above specified method was applied to
	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP [3] is
	a feed forward artificial neural network model that maps sets of input data
	into a set of appropriate output. It is known as feed forward because it
	does not contain any cycles and network output depends only on the current
	input instance. In MLP, each node is a neuron with a nonlinear activation
	function. It is based on supervised learning technique. Learning take place
	by changing connection weights after each piece of data is processed, based
	on the amount of error in the target output as compared to the expected
	result. The goal of the learning procedure is to minimize error by improving
	the current values of the weight associated with each edge. Because of this
	backward changing process of the weights, model is named as
	back-propagation.

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

% bibliography
\usepackage{url}
\usepackage[
	backend=biber,
	style=numeric,
	%citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

			\begin{equation}
				E = \sum^{N_g - 1}_{i=0} \sum^{N_g - 1}_{j=0} p(i, j)^2 \
				\textnormal{ here, range = [0, 1] }
			\end{equation}

@@

			\begin{equation}
				Con = \sum^{N_g -1}_{n=0} n^2 \sum^{N_g -1}_{i=0} \sum^{N_g
				-1}_{j=0} p(i,j)^2 \
				\textnormal{ here, range = [0, 1] }
			\end{equation}

@@

			\begin{equation}
				C = \frac{1}{\sigma^x \sigma^y}
				\sum^{N_g - 1}_{i=0} \sum^{N_g -1}_{j=0} (i,j) p(i,j)^2
				- \mu_x \mu_y \ \textnormal{here, range = [-1, 1]}
			\end{equation}

@@

	The Machine learning algorithms are used for
	classification of MR brain image either as normal or abnormal.  The major
	aim of ML algorithms is to automatically learn and make intelligent
	decisions. The feature set formed by above specified method was applied to
	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP is
	a feed forward artificial neural network model that maps sets of input data
	into a set of appropriate output. It is known as feed forward because it
	does not contain any cycles and network output depends only on the current
	input instance. In MLP, each node is a neuron with a nonlinear activation
	function. It is based on supervised learning technique. Learning take place
	by changing connection weights after each piece of data is processed, based
	on the amount of error in the target output as compared to the expected
	result. The goal of the learning procedure is to minimize error by improving
	the current values of the weight associated with each edge. Because of this
	backward changing process of the weights, model is named as
	back-propagation.

@@

	For classification three models are used; \textbf{CNN}, \textbf{VGG 16} and
	\textbf{Resnet 50}.

	\subsection{Convolutional Neural Network}%
	\label{sub:Convolutional Neural Network}

	CNN or Convolutional Neural Network a class of artificial neural network,
	most commonly applied to analyze visual imagery.They are also known as
	shift invariant or space invariant artificial neural networks (SIANN), based
	on the shared-weight architecture of the convolution kernels or filters that
	slide along input features and provide translation equivariant responses
	known as feature maps. Counter-intuitively, most convolutional neural
	networks are only equivariant, as opposed to invariant, to translation.
	They have applications in image and video recognition, recommender
	systems, image classification, image segmentation, medical image
	analysis, natural language processing, brain-computer interfaces, and
	financial time series.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.8\linewidth]{imgs/cnn_arch.png}
		\caption{CNN architecture}%
		\label{CNN Architecture}
	\end{figure}

	\subsubsection{Architecture}

	A convolutional neural network consists of an input layer, hidden layers and
	an output layer. In any feed-forward neural network, any middle layers are
	called hidden because their inputs and outputs are masked by the activation
	function and final convolution. In a convolutional neural network, the
	hidden layers include layers that perform convolutions. Typically this
	includes a layer that performs a dot product of the convolution kernel with
	the layer's input matrix.  This product is usually the Frobenius inner
	product, and its activation function is commonly ReLU. As the convolution
	kernel slides along the input matrix for the layer, the convolution
	operation generates a feature map, which in turn contributes to the input of
	the next layer. This is followed by other layers such as pooling layers,
	fully connected layers, and normalization layers \cite{covnet_arch}.

	\textbf{Convolutional Layer}:
	In a CNN, the input is a tensor with a shape: (number of inputs) x (input
	height) x (input width) x (input channels). After passing through a
	convolutional layer, the image becomes abstracted to a feature map, also
	called an activation map, with shape: (number of inputs) x (feature map
	height) x (feature map width) x (feature map channels). A convolutional
	layer within a CNN generally has the following attributes:

	\begin{itemize}
		\item Convolutional filters/kernels defined by a width and height (hyper-parameters).
		\item The number of input channels and output channels
			(hyper-parameters). One layer's input channels must equal the number
			of output channels (also called depth) of its input.
		\item Additional hyperparameters of the convolution operation, such as:
			padding, stride, and dilation.
	\end{itemize}

	Convolutional layers convolve the input and pass its result to the next
	layer. This is similar to the response of a neuron in the visual cortex to a
	specific stimulus.

	\textbf{Pooling Layer}:
	Convolutional networks may include local and/or global pooling layers along
	with traditional convolutional layers. Pooling layers reduce the dimensions
	of data by combining the outputs of neuron clusters at one layer into a
	single neuron in the next layer. Local pooling combines small clusters,
	tiling sizes such as 2 x 2 are commonly used. Global pooling acts on all the
	neurons of the feature map. There are two common types of pooling in popular
	use: max and average. Max pooling uses the maximum value of each local
	cluster of neurons in the feature map, while average pooling takes the
	average value.

	\textbf{ReLU Layer}:

	ReLU is the abbreviation of rectified linear unit, which applies the
	non-saturating activation function
	\begin{equation}
		f ( x ) = \max ( 0 , x )
	\end{equation}

	.It effectively removes
	negative values from an activation map by setting them to zero. It
	introduces nonlinearities to the decision function and in the overall
	network without affecting the receptive fields of the convolution layers.

	Other functions can also be used to increase nonlinearity, for example the
	saturating hyperbolic tangent
	\begin{equation}
	f(x)=\tanh(x)
	f(x) = | \tanh (x) |
	\end{equation}
	and the
	sigmoid function

	\begin{equation}
		\sigma(x) = (1+e^{-x})^{-1}
	\end{equation}

	ReLU is often preferred to other functions because it trains the neural network several
	times faster without a significant penalty to generalization accuracy
	 \cite{relu_layer}.

	\textbf{Fully Connected Layer}

	After several convolutional and max pooling layers, the final classification
	is done via fully connected layers. Neurons in a fully connected layer have
	connections to all activations in the previous layer, as seen in regular
	(non-convolutional) artificial neural networks. Their activations can thus
	be computed as an affine transformation, with matrix multiplication followed
	by a bias offset (vector addition of a learned or fixed bias term).

	\textbf{Loss Layer}

	The "loss layer", or "loss function", specifies how training penalizes the
	deviation between the predicted output of the network, and the true data
	labels (during supervised learning). Various loss functions can be used,
	depending on the specific task.

	The Softmax loss function is used for predicting a single class of K
	mutually exclusive classes. Sigmoid cross-entropy loss is used for
	predicting K independent probability values is $[0, 1]$.  Euclidean loss is
	used for regressing to real-valued labels $(- \infty, \infty)$.

	\textbf{Receptive field}

	In neural networks, each neuron receives input from some number of locations
	in the previous layer. In a convolutional layer, each neuron receives input
	from only a restricted area of the previous layer called the neuron's
	receptive field. Typically the area is a square (e.g. 5 by 5 neurons).
	Whereas, in a fully connected layer, the receptive field is the entire
	previous layer. Thus, in each convolutional layer, each neuron takes input
	from a larger area in the input than previous layers. This is due to
	applying the convolution over and over, which takes into account the value
	of a pixel, as well as its surrounding pixels. When using dilated layers,
	the number of pixels in the receptive field remains constant, but the field
	is more sparsely populated as its dimensions grow when combining the effect
	of several layers.

	\textbf{Weights}

	Each neuron in a neural network computes an output value by applying a
	specific function to the input values received from the receptive field in
	the previous layer. The function that is applied to the input values is
	determined by a vector of weights and a bias (typically real numbers).
	Learning consists of iteratively adjusting these biases and weights.

	The vector of weights and the bias are called filters and represent
	particular features of the input (e.g., a particular shape). A
	distinguishing feature of CNNs is that many neurons can share the same
	filter. This reduces the memory footprint because a single bias and a single
	vector of weights are used across all receptive fields that share that
	filter, as opposed to each receptive field having its own bias and vector
	weighting.

	%\subsection{VGG 16}

	\section[implementation]{\hfill \Huge Implementation \hfill}

	\subsection{Assumptions and Dependencies}%
	\label{sub:Assumptions and Dependencies}
	It is assumed that the MRI scans are collected and processed before feeding
	into the module.

	The program is dependent on external modules and are expected to be
	pre-installed on the system. The modules namely include:

	\begin{itemize}
		\item \href{https://www.fast.ai/}{fast.ai}
		\item \href{https://www.tensorflow.org/}{tensorflow}
		\item \href{https://opencv.org/}{OpenCV}
		\item \href{https://matplotlib.org/}{matplotlib}
	\end{itemize}

	\subsection{Implementation Methods}%
	\label{sub:Implementation Methods}
	After acquiring the data, the data is classified into two classes (binary
	class) of yes, consisting of tumorous cell and no, not consisting tumorous
	cells. A second batch of images is kept separate for prediction, the
	prediction batch.

	Next three machine learning models are created. A \textbf{CNN} or a
	convolutional neural network, \textbf{VGG 16} and \textbf{Resnet 50}.
